P versus NP

### 2020-01-07 doc/manuscript.tex
Updated doc.

For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$? In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least two consecutive pair of nodes in the sequence where they are not connected by an edge.

@@

\begin{definition}
$\textbf{MAXIMUM EXCLUSIVE-OR 2-SATISFIABILITY}$

>>>>

For example, there is a well-known $coNL$ problem that states: Given a directed graph $G = (V, E)$ and two nodes $s, t \in V$, is there no possible path from $s$ to $t$? In that problem, an appropriated disqualification $u$ is a sequence of nodes contained in $V$ when $s$ is the first node and $t$ is the last one such that this sequence of nodes is not a path: There is at least a consecutive pair of nodes in the sequence where they are not connected by an edge.

@@

\begin{definition}
$\textbf{MAXIMUM EXCLUSIVE-OR 2SAT}$
